### 2017-06-18 src/hardness.tex
fix errors
problem + hardness

The VPN problem, in its general form, can not be approximated at all.
To see this, consider an instance of the problem where the virtual graph is a simple path of $n = |V_p|$ vertices, $p_d \equiv p_c \equiv 1$, 
$b_d \equiv b_c \equiv 1$,
and $c \equiv 0$.
In this instance any feasible embedding has cost 0, furthermore, one exists if and only if there is an Hamiltonian path in the physical graph.
Thus, any algorithm that returns a feasible embedding also finds an Hamiltonian path.

We also show that the problem remains NP-hard even when restricted to DAGS.

Consider the problem in its general form. 
Given an undirected graph $G$
\todo{finish}

We now show that the problem restricted to DAG is still NP-hard.
We present a polynomial reduction from partition.
Let $\{a_1, \ldots, a_n\}$ be an instance of the partition problem, 
consider the instance of the VPN problem 
$D_v = (V_v, A_v), D_p = ({v}, \emptyset)$, 
where:
\begin{align}
V_v = \{s, t\} \cup \{v_1^+, \ldots, v_n^+\} \cup \{v_1^-, \ldots, v_n^-\}
\\
A_v = \{\{v_i^+, v_i^-\} \times \{v_{i + 1}^+, v_{i + 1}^-\}\} 
\cup \{(s, v_1^+), (s, v_1^-), (v_n^+, t), (v_n^-, t)\}
&&
\forall i \in [n-1]
\\
p_d(v_i^+) = a_i && \forall i \in [n]
\\
p_d(v_i^-) = 0 && \forall i \in [n]
\\
c(v_i^+, v) = 0 && \forall i \in [n]
\\
c(v_i^-, v) = a_i && \forall i \in [n] 
\\
p_c(v) = \frac{1}{2}\sum_{i = 1}^n a_i
\end{align}
Note that the bandwidth function does not plays a role here because the physical graph
is just a single vertex.

@@

\todo{finish}

>>>>

In this section we show that even the feasibility decision problem, 
i.e. deciding if there is a feasible embedding given a request graph and a
physical network, 
is NP-hard.
This implies that the problem cannot be (multiplicatively) approximated at all.  
To see this, 
consider an instance of the problem where the virtual graph is a simple path of 
$n = |V_p|$ vertices, 
$p_d \equiv p_c \equiv 1$, 
$b_d \equiv b_c \equiv 1$,
and $c \equiv 0$.
In this instance any feasible embedding has cost 0, 
furthermore, 
one exists if and only if there is an Hamiltonian path in the physical graph.
Thus, any algorithm that returns a feasible embedding also finds an Hamiltonian path.

We also show that the problem remains NP-hard even when the request graph is
acyclic.
We present a polynomial reduction from the \textsc{partition problem}.
Let $\{a_1, \ldots, a_n\}$ be an instance of the partition problem, 
consider the instance of the VPN problem 
$D_v = (V_v, A_v), D_p = ({v}, \emptyset)$, 
where:
\begin{align}
V_v = \{s, t\} \cup \{v_1^+, \ldots, v_n^+\} \cup \{v_1^-, \ldots, v_n^-\}
\\
A_v = \{\{v_i^+, v_i^-\} \times \{v_{i + 1}^+, v_{i + 1}^-\}\} 
\cup \{(s, v_1^+), (s, v_1^-), (v_n^+, t), (v_n^-, t)\}
&&
\forall i \in [n-1]
\\
p_d(v_i^+) = a_i && \forall i \in [n]
\\
p_d(v_i^-) = 0 && \forall i \in [n]
\\
c(v_i^+, v) = 0 && \forall i \in [n]
\\
c(v_i^-, v) = a_i && \forall i \in [n] 
\\
p_c(v) = \frac{1}{2}\sum_{i = 1}^n a_i
\end{align}
Note that the bandwidth function does not plays a role here because the physical graph
is just a single vertex.

@@

### 2017-06-18 src/problem.tex
problem + hardness

In the Service Chain Placement in SDN problem the goal is to find a
feasible embedding of a virtual path into the physical DAG that minimizes the
cost.

\begin{figure}[ht]
\centering
\scalebox{.8}{
\input{fig-embedding}
}

\end{figure}

>>>>

In the \VPN problem the goal is to find a
feasible embedding of a virtual path into the physical DAG that minimizes the
cost.
Figure~\ref{fig:problem} illustrate an embedding of a virtual request into a
physical network.

\begin{figure}[ht]
\centering
\scalebox{.8}{
\input{fig-embedding}
}
\caption{
An embedding of a graph representation of a virtual request (on the left) into
the physical network (on the right).
The source and destination vertices are dashed, as well as the chosen virtual
path.
The numbers on the vertices represent the processing demand and capacity
respectively, 
the numbers on the edges represent the bandwidth demand and capacity
respectively.
The partition of the virtual path and its embedding are marked by the orange,
dotted arrows.
The cost function is not depicts in this figure.
\label{fig:problem}
}
\end{figure}
